A JSDM with zero-inflation to increase the ecological relevance of analyses of species distribution data.

### 2025-07-24 PAPER_CODE.qmd
cleaned up code for submission

---
title: "Species association networks unveil scale effects in community assemblage mechanisms."
author: "Jeanne Tous, Julien Chiquet"
format: html
editor: visual
---

@@

```{r, loading libraries}
# library(PLNmodels)
library(Metrics)
library(pheatmap)
library(tidyverse)
library(FactoMineR)
library(factoextra)
library(viridisLite)
```

@@

color_palette <- paletteer_c("ggthemes::Orange-Gold", n = 30)
palette_colors <- paletteer::paletteer_c("ggthemes::Orange-Gold", n = 29)  # 29 instead of 30
color_palette <- c("white", palette_colors)
max_val <- max(log_abundance_sorted, na.rm = TRUE)

@@

```{r baselines-data-formatting}
nb_pc <- ncol(NR_COVARIATES) - 4
NR_PCA <-
  NR_COVARIATES %>%
  PCA(quali.sup = quali_ind, ncp = nb_pc, scale.unit = TRUE, graph = FALSE)

@@

covariates = cbind(NR_COVARIATES, NR_PCA_SCORES)
NR_DATA <- prepare_data(
  counts     = NR_COUNTS,
  covariates = covariates
)
covar_data <- NR_DATA %>% select(c("PC1", "PC2", "disturbance", "stream"))
```

>>>>

---
title: "A JSDM with zero-inflation to increase the ecological relevance of analyses of species distribution data."
author: "Jeanne Tous, Julien Chiquet, Amy E. Deacon, Ada Fontrodona-Eslava, Douglas F. Fraser, Anne E. Magurran"
format: html
editor: visual
---

@@

```{r, loading libraries}
library(PLNmodels)
library(Metrics)
library(pheatmap)
library(tidyverse)
library(FactoMineR)
library(factoextra)
library(viridisLite)
```

@@

color_palette  <- paletteer::paletteer_c("ggthemes::Orange-Gold", n = 30)
palette_colors <- paletteer::paletteer_c("ggthemes::Orange-Gold", n = 29)  # 29 instead of 30
color_palette <- c("white", palette_colors)
max_val <- max(log_abundance_sorted, na.rm = TRUE)

@@

```{r baselines-data-formatting}
nb_pc <- ncol(NR_COVARIATES) - 4

NR_PCA <-
  NR_COVARIATES %>%
  PCA(quali.sup = quali_ind, ncp = nb_pc, scale.unit = TRUE, graph = FALSE)

@@

covariates = cbind(NR_COVARIATES, NR_PCA_SCORES)
NR_DATA <- prepare_data(
  counts     = NR_COUNTS,
  covariates = covariates
)
covar_data <- NR_DATA %>% dplyr::select(c("PC1", "PC2", "disturbance", "stream"))
```
